Supplement to Initial estuarine response to the nutrient dense Piney Point wastewater discharge into Tampa Bay, Florida

### 2021-10-17 manu-draft.Rmd
nutrient flow figure and supp fo figure done

>>>>

```{r nutrientflow, fig.cap = 'Weekly summarized observations (medians, 2.5th to 97.5th percentiles) across all sampled locations for (a) total nitrogen concentrations, (b) chlorophyll-a concentrations, (c) diatom cell concentrations, (d) *Karenia brevis* cell concentrations, and (e) cyanobacteria macroalgal abundances.  Values are summarized for all samples within each week.  The values suggest nutrient cycling between water column phytoplankton in the initial April diatom bloom, then to cyanobacteria macroalgae in May to June, and then to *K. brevis* peaking in early July. Quantitative cell counts for diatoms are missing for several weeks, but see supplementary figures for frequency occurence estimates across all dates.  Diatom concentrations are based on combined cell counts from *Asterionellopsis sp.* and *Skeletonema sp*.'}
knitr::include_graphics('figs/nutrientflow.jpeg')
```

### 2021-10-17 supplement.Rmd
nutrient flow figure and supp fo figure done

>>>>

```{r phymcrfoest, fig.cap = 'Frequency occurrence estimates for (a) phytoplankton (diatoms and *K. brevis*) and (b) macroalgae groups. Frequency occurrence estimates are aggregated by week of observation based on all sample locations where a phytoplankton or macroalgal taxa was observed divided by all sample locations in a week.  Estimates are not additive and are specific to each taxa.  Sample dates are noted by vertical grey lines in each plot. Diatoms are based on presence/absense of *Asterionellopsis sp*. and *Skeletonema sp*.  Note that frequency occurrence is not a precise measure of cell concentrations.'}
knitr::include_graphics('figs/phymcrfoest.jpeg')
```
